---
title: "Coding document - R intermediate course DDEA 2026"
author: "KSV"
format: html
---
µ
## Loading packages
An "r setup"-code chunk is always the first chunck from a Quarto-document that will be run when other chunks of the document are run.
Here package can help maintain the project from within.
```{r setup}
#| include: false
library("tidyverse")
library("here")
library("snakecase")
library("fs")
source(here("R/functions.R"))
```

##Importing nurses-stress data
The difference between the read_csv and read.csv is that the read_csv is more controlled and belongs to the tidyverse
.
```{r}
#| eval: false
here("data-raw/nurses-stress/stress/5C/5C_1586886626/HR.csv.gz") %>% # By using the 'here' function we are telling R to where the file is currently at ... Helps reproducability.
  read_csv(
    show_col_types = FALSE, # removes the R assumed types of data in each column, which would otherwise be listed under the dataoutput visual.
    name_repair = to_snake_case, # snake_case is a way to reformat the coloumn-names to use _ instead of Uppercases to distinguish words where a usual space would used. We introduce the package for snake_case in setup-chunk.
    n_max = 100 # limits number of rows loaded
  )

# ? before a function name get the description of the funciton in the Help-section.

# It is a good idea to t %>% est code by loading short part of large dataset, then test code, then use the full dataset to run code and final functions. We alter the n_max part of read_csv-function
```

## Exercise: Reading other files


```{r}
#| eval: false
here("data-raw/nurses-stress/stress/5C/5C_1586886712/HR.csv.gz") %>%
  read_csv(
    show_col_types = FALSE,
    name_repair = to_snake_case,
    n_max = 100
  )

here("data-raw/nurses-stress/stress/6B/6B_1587569373/EDA.csv.gz") %>%
  read_csv(
    show_col_types = FALSE,
    name_repair = to_snake_case,
    n_max = 100
  )
```


##How to make a function (ultimately to load files similarly automatically, here as a simple example)

```{r}
#' Addition of two numbers #This is the title of the Roxygen
#'
#' @param num1 The first number added
#' @param num2 The second number added
#'
#' @returns Gives the sum of two numbers #A description of what the function returns

# @export #Also part of the Roxygen. Mostly useful for making a package, tells people if the function should be available to them

# @examples #Also part of the Roxygen. Useful for showing how to use the function in a package.

add_numbers <- function(num1, num2) {
  output <- num1 + num2
  return(output)
}
# Husk ikke at have curseren inde i funktionen når du kører den. Til at indsætte Roxygenobjekt, skal Crtl+shift+P and choose Insert Roxygen
# Render means reforming R to a differetnt format like HTML, will also check if all functions are working.
add_numbers(66, 2)
```

##We are adding a function for loading files
```{r}
#| eval: false
here("data-raw/nurses-stress/stress/5C/5C_1586886626/HR.csv.gz") %>%
  read_csv(
    show_col_types = FALSE,
    name_repair = to_snake_case,
    n_max = 100
  )

# To make it a function

?read # Tests if a function name is already in use by some R packages

read <- function() {
  here("data-raw/nurses-stress/stress/5C/5C_1586886626/HR.csv.gz") %>%
    read_csv(
      show_col_types = FALSE,
      name_repair = to_snake_case,
      n_max = 100
    )
}

# Make it more generic by replacing specific elements with arguments that can be replaced by specific things when using the function

#' Read CSV-datatables in R
#'
#' @param file_path The specific path to the CSV-datafile
#'
#' @returns A CSV-datatable in R format as a tibble
read <- function(file_path) {
  data <- file_path %>%
    read_csv(
      show_col_types = FALSE,
      name_repair = to_snake_case,
      n_max = 100
    )
  return(data)
} # REMEMBER TO PLACE CURSER OUTSIDE THE CODE!! OTHERWISE IT WONT WORK!!
```

Testing the new read function:
```{r}
#| output: false
here("data-raw/nurses-stress/stress/5C/5C_1586886626/HR.csv.gz") %>%
  read()

here("data-raw/nurses-stress/stress/5C/5C_1586886712/HR.csv.gz") %>%
  read()
```


##Adjusting the read function 
```{r}
#| eval: false
# eval: false Added as we moved the function to the functions-document.
#' Read CSV-datatables in R
#'
#' @param file_path The specific path to the CSV-datafile
#'
#' @param file_path The specific path to the CSV-datafile
#' @param max_rows The maximum number of rows included in the tibble
#' @returns A CSV-datatable in R format as a tibble

read <- function(file_path, max_rows = 100) {
  data <- file_path %>%
    readr::read_csv( # We add which package the read_csv comes from and this will automatically be used when running the function. Don't use library(PACKAGE NAME) or require(PACKAGE NAME) as it can ruin later functionality of the function.
      show_col_types = FALSE,
      name_repair = snakecase::to_snake_case,
      n_max = max_rows,
    )
  return(data)
}


# Testing it:
# Outputs only 100 rows
here("data-raw/nurses-stress/stress/5C/5C_1586886712/HR.csv.gz") |>
  read()

# Outputs only 1000 rows
here("data-raw/nurses-stress/stress/5C/5C_1586886712/HR.csv.gz") |>
  read(max_rows = 1000)

# Outputs all rows (`Inf` means infinity)
here("data-raw/nurses-stress/stress/5C/5C_1586886712/HR.csv.gz") |>
  read(max_rows = Inf)
```

##Making robust and reuseable functions
The usethis::use_package("XX") will check if the package is installed otherwise install it. 
The usethis::use_tidy_description may include version number or usethis::use_tidy_dependencies. 
```{r}
# usethis::use_tidy_description
# usethis::use_tidy_dependencies
# It is the _dependencies.
#| #output:false #this will remove the tibble from the rendered file.
```

Now we describe what parts of the function comes from which packages and only using a specific package function. 

##Adding functions to an R function.R-file
```{r}
# CRTL. to open the functionsfile.
# Now we simply cut and paste
```

##Day 2: Functionals (repeated functions automatically to vectors
We are using the package fs to create an overall filepath for all the nested files in folders for the nurses-stress-dataset. The argument 'recurse' (looking in all subfolders) and 'regexp' from the function dir_ls ('Within this folder tell me the name of all the files) to do this
```{r}
hr_files <- here("data-raw/nurses-stress/") |> # Gonna pipe this path in the dir_ls
  dir_ls(regex = "HR.csv.gz", recurse = TRUE)

hr_data <- hr_files |>
  map(read) # This just creates a list of all the files as tibbles, not an actual dataframe.
```
Before it can be row-combind it to a dataframe, we'll need to add ID for all the nurses before. 
```{r}
hr_data_all <- hr_data |>
  list_rbind(names_to = "file_path_id") # Adds file_path_id as ID, we will then extract the actual ID and only keep this as the ID-number.

# Adding all the other types of data

unique(hr_data_all$file_path_id)
```

##Exercise: Convert map to function and use on sleep
```{r}
#| output= false
#' Functional to read in multiple files to dataframe at once from the same mother-folder
#'
#' @param filename Name of the files that should be added to the dataframe from all the subfolders
#'
#' @returns A dataframe combining multiple files from different subfolders

read_all <- function(filename, max_rows = 100) {
  files <- .DATASET_DIR |>
    fs::dir_ls(regexp = filename, recurse = TRUE)
  data <- files |>
    purrr::map(\(file) read(file, max_rows = max_rows)) |>
    purrr::list_rbind(names_to = "file_path_id")
  return(data)
}

read_all("HR.csv.gz")
```

## Datainspection - quantitative and qualitative data
```{r}
#| output= false

survey_data <- here("data-raw/nurses-stress/survey-results.csv/survey-results.csv") |>
  read()

hr_data_all

survey_data
unique(survey_data$id)
unique(hr_data_all$file_path_id)
```
```{r}
hr_data_all |>
  mutate(
    ID = str_extract( # Extracts complete match from the argument below
      file_path_id,
      pattern = "/stress/[:alnum:]{2}/"
    ) |>
      str_remove("/stress/") |> # First remove the stress-folder-name
      str_remove("/"), # Then removing the two backlashes, as these characters could not be removed along with the stress-name
    .before = file_path_id # Tells R to place the new column before the current column called file_path_id
  ) |>
  select(!c(file_path_id))
```

## Create function to extract participant ID
```{r}
get_participant_id <- function(data) {
  data_with_id <- data |>
    dplyr::mutate(
      ID = stringr::str_extract( # Extracts complete match from the argument below
        file_path_id,
        pattern = "/stress/[:alnum:]{2}/"
      ) |>
        stringr::str_remove("/stress/") |> # First remove the stress-folder-name
        stringr::str_remove("/"), # Then removing the two backlashes, as these characters could not be removed along with the stress-name
      .before = file_path_id # Tells R to place the new column before the current column called file_path_id
    ) |>
    dplyr::select(!c(file_path_id))
  return(data_with_id)
}

?select

read_all("BVP.csv.gz") |>
  get_participant_id()
```
