---
title: "Draft Quarto document"
author: "KSV"
format: html
---
µ
## Loading packages
An "r setup"-code chunk is always the first chunck from a Quarto-document that will be run when other chunks of the document are run.
Here package can help maintain the project from within.
```{r setup}
#| include: false
library("tidyverse")
library("here")
library("snakecase")
```

##Importing nurses-stress data
The difference between the read_csv and read.csv is that the read_csv is more controlled and belongs to the tidyverse
.
```{r}
here("data-raw/nurses-stress/stress/5C/5C_1586886626/HR.csv.gz") %>% # By using the 'here' function we are telling R to where the file is currently at ... Helps reproducability.
  read_csv(
    show_col_types = FALSE, # removes the R assumed types of data in each column, which would otherwise be listed under the dataoutput visual.
    name_repair = to_snake_case, # snake_case is a way to reformat the coloumn-names to use _ instead of Uppercases to distinguish words where a usual space would used. We introduce the package for snake_case in setup-chunk.
    n_max = 100 # limits number of rows loaded
  )

# ? before a function name get the description of the funciton in the Help-section.

# It is a good idea to t %>% est code by loading short part of large dataset, then test code, then use the full dataset to run code and final functions. We alter the n_max part of read_csv-function
```

## Exercise: Reading other files


```{r}
here("data-raw/nurses-stress/stress/5C/5C_1586886712/HR.csv.gz") %>%
  read_csv(
    show_col_types = FALSE,
    name_repair = to_snake_case,
    n_max = 100
  )

here("data-raw/nurses-stress/stress/6B/6B_1587569373/EDA.csv.gz") %>%
  read_csv(
    show_col_types = FALSE,
    name_repair = to_snake_case,
    n_max = 100
  )
```


##How to make a function to load files similarly automatically

```{r}
#' Addition of two numbers #This is the title of the Roxygen
#'
#' @param num1 The first number added
#' @param num2 The second number added
#'
#' @returns Gives the sum of two numbers #A description of what the function returns

# @export #Also part of the Roxygen. Mostly useful for making a package, tells people if the function should be available to them

# @examples #Also part of the Roxygen. Useful for showing how to use the function in a package.

add_numbers <- function(num1, num2) {
  output <- num1 + num2
  return(output)
}
# Husk ikke at have curseren inde i funktionen når du kører den. Til at indsætte Roxygenobjekt, skal Crtl+shift+P and choose Insert Roxygen
# Render means reforming R to a differetnt format like HTML, will also check if all functions are working. 
add_numbers(66, 2)
```
